Structured Versus Decorated Cospans

### 2020-11-25 cospans.tex
fixed typos in bibliography

\bibitem{CV} D.\ Cicala and C.\ Vasilakopoulou, On Adjoints and fibrations. In preparation.

@@

\bibitem{Gray} J. \ Gray, Fibred and cofibred categories, \textsl{Proc.\ Conf.\ Categorical Algebra} (La Jolla, California, 1965), 21---83, New York, 1966

@@

\bibitem{RSW} R.\ Rosebrugh, N.\ Sabadini and R.\ F.\ C.\ Walters, Generic commutative separable algebras and cospans of graphs, \textsl{Theory Appl. Categ.} \textbf{15} (2005), 164--177. Available at \href{http:/.www.tac.mta.ca/tac/volumes/15/6/15-06.pdf}{http:/.www.tac.mta.ca/tac/volumes/15/6/15-06.pdf}.

@@

\bibitem{Shulman2008} M.\ Shulman, Framed bicategories and monoidal fibrations, \textsl{Theory Appl.Categ.} \textbf{20} (2008), 650--738. Available as \href{https://arxiv.org/abs/0706.1286}{arXiv:0706.1286}.

>>>>

\bibitem{CV} D.\ Cicala and C.\ Vasilakopoulou, On adjoints and fibrations. In preparation.

@@

\bibitem{Gray} J. \ Gray, Fibred and cofibred categories, \textsl{Eilenberg, Samuel, et al., eds. Proceedings of the Conference on Categorical Algebra: La Jolla 1965},  Springer, Berlin, 1966, pp.\ 21--83.

@@

\bibitem{RSW} R.\ Rosebrugh, N.\ Sabadini and R.\ F.\ C.\ Walters, Generic commutative separable algebras and cospans of graphs, \textsl{Theory Appl.\ Categ.\ }\textbf{15} (2005), 164--177. Available at \href{http:/.www.tac.mta.ca/tac/volumes/15/6/15-06.pdf}{http:/.www.tac.mta.ca/tac/volumes/15/6/15-06.pdf}.

@@

\bibitem{Shulman2008} M.\ Shulman, Framed bicategories and monoidal fibrations, \textsl{Theory Appl.\ Categ.\ }\textbf{20} (2008), 650--738. Available as \href{https://arxiv.org/abs/0706.1286}{arXiv:0706.1286}.
